Response to the defense feedback

### 2021-06-03 Chapter-5/Chapter-5.tex
Updates from Overleaf

Even a minor leakage can be severe for cryptography libraries because
the leakage can reduce the encryption algorithm's strength. However,
some attacks also exploit non-cryptography libraries and applications
such as machine learning
applications~\cite{yan2020cache,hong2018security}, graphic
libraries~\cite{wang2019unveiling}, spell checking
tools~\cite{xu2015controlled}, etc. Unlike side-channel attacks on
cryptography libraries that exploit one vulnerability at a time,
attacks on non-cryptography rely on multiple side-channel leakage
sites to retrieve more information. Suppose a program has two
leakage sites. It is hard to estimate the total effect of those two
leakages. However, no existing tools that can estimate the total
effect of multiple leakage sites. For real-world applications with
thousands of lines, it is hard to estimate the amount of leaked
information. Attackers can guess the values of some temporary
values. And those temporary values contain some knowledge of the
original secret buffer.

@@

We rely on the program header and symbol information to recover the
offset in the binary. During the loading process, the operating system
maps each segment into a contiguous memory region. So the offset of
the virtual memory address between the code within the same segment is
the same as the offset within the binary file. We choose the start
address of some common functions (e.g, $\mathit{main}$) ($b$) as the navigation
function. We get the virtual memory address of the start of the
function ($\mathit{VMA}_b$) from the DBI tool and the load memory
address of the function ($\mathit{LMA}_b$) from the symbol
information. For any virtual address, we use Equation~\ref{equ:eq6} to
calculate the offset in the original address.
\begin{equation}\label{equ:eq6}
    \mathit{LMA}_a = \mathit{LMA}_b - \mathit{VMA}_b - \mathit{VMA}_a
\end{equation}

>>>>

Even a minor leakage can be severe for cryptography libraries because
the leakage can reduce the encryption algorithm's strength. However,
some attacks also exploit non-cryptography libraries and applications
such as machine learning
applications~\cite{yan2020cache,hong2018security}, graphic
libraries~\cite{wang2019unveiling}, spell checking
tools~\cite{xu2015controlled}, etc. Unlike side-channel attacks on
cryptography libraries that exploit one vulnerability at a time,
attacks on non-cryptography rely on multiple side-channel leakage
sites to retrieve more information. A program  usually has more than two
leakage sites. However, no existing tools that can estimate the total
effect of multiple leakage sites. For real-world applications with
thousands of lines, attacker can exploit more than one leakage sites
to retrieve more information. Attackers can guess the values of many temporary
values. And these temporary values contain some knowledge of the
original secret buffer.

@@

We rely on the program header and symbol information to recover the
offset in the binary. During the loading process, the operating system
maps each segment into a contiguous memory region. So the offset of
the virtual memory address between the code within the same segment is
the same as the offset within the binary file. We choose the start
address of some common functions (e.g., $\textsf{main}$) ($b$) as the navigation
function. We get the virtual memory address of the start of the
function ($\mathit{VMA}_b$) from the DBI tool and the load memory
address of the function ($\mathit{LMA}_b$) from the symbol
information. For any virtual address, we use Equation~\ref{equ:eq6} to
calculate the offset in the original address.
\begin{equation}\label{equ:eq6}
    \mathit{LMA}_a = \mathit{LMA}_b - \mathit{VMA}_b - \mathit{VMA}_a
\end{equation}
